Project Contract\\Local Adaptive Optimization of Timestep

### 2013-09-04 report/report.tex
First draft of project contract

\subsection{Motivation}

\subsection{Proposed solution}

\subsection{Success criteria}

\subsection{Risk assessment}

>>>>

\subsection{Motivation}
When running a simulation of large hyperelastic materials we wish to make
large enough steps for the simulation to be performed within a reasonable
timeframe, but we still want the simulation to be accurate and to avoid
the mesh from curling up or exploding due to too large determinants of the
moving mesh vertices. In some hyperelastic materials most of the
discretized points are able to be simulated using larger timesteps whereas
smaller areas might need smaller timesteps. These situations are the ones
we wish to accomodate in this paper.

\subsection{Proposed solution}
We wish to develop a method for locally adapting the timestep size in
order to avoid curl ups/explosions while still maintaining the original
timestep size of the rest of the simulation. In other words for each of
the original timesteps we perform further simulations of problematic local
areas of the grid with smaller timesteps.

\subsection{Success criteria}
Avoid curl ups/explosions of the grid while maintaining the original
stepsize by using local subsimulations (with smaller stepsizes)

\subsection{Risk assessment}
Low. The technique has been performed before in various shapes and it
should therefore be do-able.
